### 2021-07-15 chapters/3_background.tex
changes
chagnes
minor style change

\chapter{Background}
\label{ch:background}
This chapter will present the necessary background information for this thesis. First, we define some basic terminology that will be used throughout this thesis.
Next, we will compare existing mutation testing tools. We start of by reviewing existing literature and then extend the comparison. 
This thesis relies on clustering techniques.
We review the state of the art on clustering algorithms and secondly the state of the art on machine learning models specialized in clustering.

\section{Terminology}
Subsuming mutants.
Mutation testing.
Levenshtein distance.
Maven.
Gradle.
Mutator.
test engine??
\section{Project selection}
\label{ch:project_selection}
We choose three main requirements for selecting software projects; the projects should have a test suite, the test suite should not contain failing tests and the mutation testing tool should be able to execute mutants for the sample project.
We selected projects that were also used in other research within the mutation testing and testing domain\cite{Pizzoleto2019,Yu2019PossibilityScope,Wei2021SpectralTesting, Zhang2019PredictiveTesting, Chen2018SpeedingStudy, Laurent2017AssessingPIT}.
\newline
We extend our sample by selecting projects from the first six pages of the most popular Java projects on GitHub\footnote{\url{https://github.com/search?p=7&q=language\%3Ajava+stars\%3A\%3E10000&type=Repositories}}.
The unfiltered sample contains 50+ projects.
From there we filter out all the projects that contain failing tests and that aren't libraries or applications.
The result consists of a sample with fifteen projects in total.

>>>>

\chapter{Background}
\label{ch:background}
This chapter presents the necessary background information for this thesis. First, we define some basic terminology that will be used throughout this thesis.
Next, we will compare existing mutation testing tools. We start of by reviewing existing literature and then extend the comparison. 
This thesis relies on clustering techniques.
We review the state of the art on clustering algorithms and secondly the state of the art on machine learning models specialized in clustering.

\section{Terminology}
Subsuming mutants.
Mutation testing.
Levenshtein distance.
Maven.
Gradle.
Mutator.
test engine.
weighted mutation score.
\section{Project selection}
\label{ch:project_selection}
We choose three main requirements for selecting software projects; the projects should have a test suite, the test suite should not contain failing tests and the mutation testing tool should be able to execute mutants for the sample project.
We selected projects that were also used in other research within the mutation testing and testing domain\cite{Pizzoleto2019,Yu2019PossibilityScope,Wei2021SpectralTesting, Zhang2019PredictiveTesting, Chen2018SpeedingStudy, Laurent2017AssessingPIT}.
\newline
We extend our sample by selecting projects from the first six pages of the most popular Java projects on GitHub\footnote{\url{https://github.com/search?p=7&q=language\%3Ajava+stars\%3A\%3E10000&type=Repositories}}.
The unfiltered sample contains 50+ projects.
From there we filter out all the projects that contain failing tests and that are not libraries or applications.
The result consists of a sample with fifteen projects in total.
